Catchy Title Goes Here

### 2018-05-23 Paper/paper.tex
injected->assumed

This Figure shows the posterior distributions and injected values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top panel is generated by analyzing all three datasets, and the bottom panel using only case and vaccination data. In addition to the injected values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top panel we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is worth nothing that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.

>>>>

This Figure shows the posterior distributions and assumed values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top panel is generated by analyzing all three datasets, and the bottom panel using only case and vaccination data. In addition to the assumed values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top panel we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is worth nothing that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.
